Fisheries management when quotas are costly to change

### 2014-07-30 manuscripts/presentation.Rmd
set output to reveal_js

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  ioslides_presentation:
    self_contained: false
    css: components/style.css
    incremental: true
transition: none
author: |
        Carl Boettiger, Michael Bode, James Sanchirico, 
        Jacob LaRiviera, Alan Hastings, Paul Armsworth

>>>>

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
#  ioslides_presentation:
#    self_contained: false
#    css: components/style.css
#    incremental: true
  revealjs_presentation:
    theme: serif
    self_contained: true
    incremental: true
    transition: none
    pandoc_args: ["--css", "style.css"]
transition: none
author: |
        Carl Boettiger, Michael Bode, James Sanchirico, 
        Jacob LaRiviera, Alan Hastings, Paul Armsworth
